Almost compatible functions and infinite length games

### 2015-12-04 articles/almost-compatible-functions-and-topological-games/article.tex
complete draft modulo Dow's results

  \begin{definition}
    A topological space is said to be \(\omega\)-bounded if each countable
    subset of the space has compact closure.
    As in \cite{MR539228} we call a
    \(T_2\), locally countable, \(\omega\)-bounded space
    \term{splendid}, and let \(\splendidS\kappa\) represent
    the claim that there exists a splendid space of cardinality \(\kappa\).
  \end{definition}

@@

  \begin{proof}
    The weaker claim
    \(\alcompS\kappa\Rightarrow\pl F \kmarkwin2\schFillIntGame\kappa\)
    was proven in \cite{clontzMengerGamePreprint};
    however, the strategy
    only required that the \(f_A\) be pairwise almost-compatible and
    that preimages of finite sets in each \(f_A\)
    are finite, which is also possible assuming \(\alcompSP\kappa\).
  \end{proof}

@@

  \section{Generalized Kurepa families and almost-compactible functions}

  TODO

>>>>

  \begin{definition}
    A topological space is said to be \term{\(\omega\)-bounded}
    if each countable subset of the space has compact closure.
    As in \cite{MR539228} we call a
    \(T_2\), locally countable, \(\omega\)-bounded space
    \term{splendid}, and let \(\splendidS\kappa\) represent
    the claim that there exists a splendid space of cardinality \(\kappa\).
  \end{definition}

@@

  \begin{proof}
    The weaker claim
    \(\alcompS\kappa\Rightarrow\pl F \kmarkwin2\schFillIntGame\kappa\)
    was proven in \cite{clontzMengerGamePreprint};
    however, the strategy
    only required that the \(f_A\) be pairwise almost-compatible and
    that preimages of finite sets in each \(f_A\)
    are finite, which is also possible assuming \(\alcompSP\kappa\).
    Note that the relationships amongst the games were all shown in
    \cite{clontzMengerGamePreprint}.
  \end{proof}

@@

  % \section{Generalized Kurepa families and almost-compactible functions}

  % TODO
